\documentclass[a4paper,10pt]{article}
\usepackage{a4wide}
\renewcommand{\labelenumi}{\alph{enumi}}
\renewcommand{\labelenumii}{\roman{enumii}}
\input{amendment-tools.tex}
%opening
\title{University of Bristol Students’ Union Anime and Science Fiction Society Constitution}
\date{2011-2012}
\begin{document}

\maketitle
\amendmentintro
\section{Name}
\begin{enumerate}
  \item The name of the Society shall be the UBU (University of Bristol Students’ Union) Anime and Science Fiction Society.
  \item The Society shall be recognised by the University of Bristol Students’ Union.
\end{enumerate}

\section{Aims}
\begin{itemize}
  \item To bring together people who share an interest in anime and/or sci-fi, for discussion and socialising.
  \item To introduce its members to new anime and sci-fi.
  \item The society shall abide by the Union’s Equal Opportunities and Harassment Policies, and any other policies laid down by the Union’s Board of Trustees.
\end{itemize}


\section{Membership}
\begin{enumerate}
  \item Full membership is open to all full members of the Union by application to the society.
  \item Associate membership is open to all other persons who are associate members of the Union.
  \item Not less than two-thirds of the Society members shall be full members of the Union.
  \item The secretary shall keep a list of all members, differentiating between full and associate members. The secretary shall inform the UBU Societies Officer of the membership of the Society each year.
  \item There shall be a subscription fee levied for membership, which shall be fixed at the discretion of the committee being no less than the minimum rate demanded by the Societies Exec. The Committee is not exempt from this membership fee.
  \item The Committee shall have the power to remove a member from their society if they believe them to have violated the Union’s Equal Opportunities and Harassment Policies, and any other policies laid down by the Union’s Board of Trustees. The decision is subject to ratification by the Societies Exec. The appeals process shall be that laid down in the Union Byelaws.
\end{enumerate}

\section{Privileges of Membership}
\begin{enumerate}
  \item Only members may sit on the committee.
  \item All categories of membership shall have equal rights of voting, attending meetings etc.
\end{enumerate}

\section{Committee}
\begin{enumerate}
  \item There shall be a society committee which shall be the executive decision making body of the society.
  \item The President of the Committee shall be a full member of the Union.
  \item The Committee shall be responsible for the general and financial policy of the Society, subject to such rules as laid out in the Union’s Constitution and Byelaws, and any rulings made by the Societies Exec.
  \item Quoracy for committee meetings shall be set at 50\% of the post filled positions plus one.
  \item All committee meetings must be minuted by the secretary (or other committee member if they are unavailable) and the minutes circulated to the committee before the next committee meeting.
  \item The committee is comprised of:
  \begin{enumerate}
    \item \textbf{President} - Responsible for General Running of the society, including arrangements for fresh and the guide entry
    \item \textbf{Vice-President} - Responsible for assisting the President and sourcing new anime, manga and Sci-Fi
    \item \textbf{Treasurer} - Responsible for organising the society finances, budgeting for events and room bookings
    \item \textbf{Secretary} - Responsible for society administration, contacting society members though E-Mail to announce meetings and events, managing the Mailing List, taking minutes at General Meetings and managing other forms of communication with the society (such as a Facebook group)
    \item \textbf{Conventions Officer} - Responsible for organising trips to Anime or Science Fiction conventions.
  \end{enumerate}
\end{enumerate}

\section{Financial}
\begin{enumerate}
  \item The Treasurer of the society shall be a full member of the Union and not in their final year at the University. However, if given approval by the UBU Societies Officer a final year student may take the position.
  \item The accounts of the Society shall be audited by a member of the Union’s staff and submitted to the UBU Societies Officer as and when requested and at least once per annum.
  \item All financial arrangements must be made in accordance with current instructions to Society Treasurers, as set down by the Societies Exec.
  \item The UBU Societies Officer and Finance Manager shall jointly be empowered to issue financial instructions on behalf of the society if:
  \begin{enumerate}
    \item the society folds with outstanding financial affairs, or
    \item change of mandate forms are not completed, and the previous Committee are out of reasonable contact, or
    \item financial irregularities are found.
  \end{enumerate}
\end{enumerate}

\section{General Meetings}
\begin{enumerate}
  \item There shall be an Annual General Meeting once per annum, and this shall be during March or April
  \item Notice of such meetings must be sent to the society’s membership via email with at least fourteen days notice. An agenda must be sent out with at least seven days notice.
  \item Quorum of such meetings shall be set at twice the committee size plus one
  \item An Extraordinary General Meeting may be called by either the Committee or 5\% of the membership of the Society by application to the Committee. An EGM shall be called as specified on the application, but at least 7 days notice shall be given.
\end{enumerate}

\section{Elections}
\begin{enumerate}
  \item Elections shall be held at the Annual General Meeting to elect officers of the committee for the following annual session. Officers can only be removed from their posts by an EGM or AGM.
  \item If committee positions are left unfilled after the AGM then the Committee shall have the power to co-opt society members onto the committee to fill the vacant posts. However, co-opted committee members are not regarded as full committee members and can be removed by the committee at any time.
  \item Voting shall be “first past the post” and shall be conducted by a show of hands with the candidates leaving the room while the vote is conducted. Only paid members may vote.
  \item After the AGM the President or Secretary must submit a sheet of contact details for the new committee to the UBU Societies Officer as soon as possible.
  \item Nominations are to be made during the AGM
  \item All General Meetings shall be chaired by an impartial non-voting member of the previous committee.
\end{enumerate}

\section{Affiliations}
\begin{enumerate}
  \item The society shall affiliate to external bodies only where membership of those bodies is essential to the fulfilment of the core aims, and only with the prior agreement of the Union’s Societies Exec.
\end{enumerate}

\section{Constitutional Amendments}
\begin{enumerate}
  \item Any amendment to this constitution shall require a two-thirds majority of the members present at a properly constituted General Meeting.
  \item All such amendments shall become valid only after approval by the Societies Exec.
\end{enumerate}

\section{Mickey}
\begin{enumerate}
  \item The society recognizes Michael John Walker as its founder and in recognition of his many years of work with the society, grants him the lifelong advisory non-committee position of “Vice-Vice-President”.
  \proposedadd{\item The society recognizes Michael John Walker as a continued influence and grants him the lifelong advisory non-committee position of Master of Contracts.}
\end{enumerate}



\end{document}
